### 2021-07-05 docs/manuscript/manuscript.tex
Rephrase text

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Mutations
included changes in the  numerical values of degradation and diffusion
parameters and interaction strengths, and addition and removal of interactions
among genes and between the genes and the morphogen. If fitness of the mutated
GRN was greater or equal than that of the previous GRN, mutated GRN was saved
and the cycle continued from step 2. This cycle was repeated 5000000 times and
GRNs with a fitness greater or equal than 0.95 were saved into a file.

@@

In order to group all the isomorphic networks in the set of 2061 GRNs we used a
classification algorithm that selected a random GRN, then it generated all
isomorphs of that GRN by performing permutations in rows and columns. The
algorithm then compared all six isomorphs with other GRN and classified the
topologies in the same group if they were isomorphic networks.

@@

Later we calculated the distance between all the pairs of tensors and we
performed a Neighbor Joining clustering using the package Scikit Bio 0.5.5 from
Python 3~\cite{skbio2020}.

@@

The average vertex degree indicates that in general, all the network topologies
display high robustness and that they could resist an average of approximately 4
topological mutations without losing their fitness. Additionally, the average
path length indicates that the evolutionary landscape is easily accessible for
most network topologies (Table~\ref{table1}). Although the GRNs in this modelling
framework are robust to changes in its topology, they are sensitive to changes in
the morphogenetic field size, especially when this size is reduced, as only
4.66, 56.82, 56.14 and 41.05 percent of the GRNs had a fitness greater than 0.9
in fields with 10, 20, 40 and 50 cells, respectively (\nameref{S3_Fig}B).

>>>>

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Mutations
included changes in the  numerical values of degradation and diffusion
parameters and interaction strengths, and addition and removal of interactions
among genes and between the genes and the morphogen. If fitness of the mutated
GRN was greater or equal than that of the previous GRN, mutated GRN was saved
and the cycle continued from step 2. This cycle was repeated 50000, and a GRN
sampled at a given step and with a fitness score ≥ 0.95 was saved to a file as
long as its associated topology had not been sampled in previous steps.

@@

In order to group all the isomorphic (i.e. topologically equivalent) networks from
the totality (2061) of sampled GRNs we used a
classification algorithm that selected a random GRN, then it generated all
isomorphs of that GRN by performing permutations in rows and columns. The
algorithm then compared all six isomorphs with other GRN and classified the
topologies in the same group if they were isomorphic networks.

@@

Next, we calculated the distance between all the pairs of tensors and performed
a Neighbor Joining clustering using the package Scikit Bio 0.5.5 from
Python 3~\cite{skbio2020}.

@@

On the other hand, analysis of the average vertex degree seems to be indicative
that network topologies are likely to withstand numerous topological
modifications (approximately 4) without significant loss in their ability to
generate a striped pattern of gene expression, representing a high fitness
solution to the prescribed task. Additionally, the average path length seems
to suggest that the evolutionary landscape could be easily traversed by
most network topologies without incurring in significant fitness loss as long
as mutational changes results in moves between adjacent neighbors across
the metagraph (Table~\ref{table1}). It is interesting to note that,
although the examined GRNs seem to exhibit, on average, a high robustness to
topological/parameter changes, they generally show a rather high sensitivity to
variation in the size of the morphogenetic field. For instance, we found that
when the size of the morphogenetic field was fixed at 10, 20, 40 and 50 cells
only 4.66\%, 56.82\%, 56.14\% and 41.05\%, respectively, of the examined
GRNs showed a fitness greater than 0.9 (\nameref{S3_Fig}B).
